PROTEST

### 2019-09-06 article/main.tex
article quick review

        \item Finally, we remove (one by one) the variables whose effect became non-significant following the addition of the quadratic effects starting with the least significant ones untill all variables were significant (see the four final species-specific models in SI).

@@

    \item First we classified the PROTEST plots into 7 compositions (corresponding to the compositions that will be simulated): 4 pure compositions (beech, oak, fir, spruce; when these species represented more than 75\% of the plots total basal area) and 3 mixed compositions (beech-fir, beech-spruce, fir-spruce; when these species were the 2 most abundant on the plots and represented (together) more than 75\% of the plots total basal area). However, because other species than our 4 target species were present on the study area (ref composition / species abundance?), we previously grouped some species together:

@@

    \item Finally, to assign a composition to a forest plot located in a specific TFV type, we randomly selected a composition from the list of compositions associated to this TFV type while complying with the composition type allready assigned to the plot (i.e. deciduous, coniferous or deciduous-coniferous mixture). Thus plots classified as deciduous could be assign 2 compositions: beech or oak; plots classified as coniferous could be assign 3 compositions: fir, spruce or fir-spruce mixture; and plots classified as deciduous-coniferous mixture could be assign 2 compositions: beech-fir or beech-spruce.

@@

\noindent We assigned species basal area values ($G_{sp}$) to each forest stand using the stand total basal area ($G_t$) and the proportion of deciduous basal area ($P_{Gd}$) calculated from LIDAR data. $G_{sp}$ could directly be derived from these measures for pure stands and deciduous-coniferous mixtures (i.e. beech-fir and beech-spruce stands). We developed a two-step procedure to assign $G_{sp}$ to conifer mixtures (i.e. fir - spruce mixtures):

@@

  \noindent where $\alpha$ and $\beta_{1-X}$ are parameters to estmiate and $\varepsilon$, the model residuals. We applied the same variable selection procedure as the one we applied to the site index model (see final model in SI). Here, we used the $G_{fir}$ and $G_{spruce}$ obtained after the grouping of species (i.e. after having assigned the basal area of non-target species to the target species; see the \textit{composition initialisation} section).

  \item We then calculated $P_{Gfir}$, the proportion of $G_{fir}$ for all conifer mixtures over the study area by adding to the model predictions a random number drawn from the normal distribution $\mathcal{N} (0, \sigma_\varepsilon)$, with $\sigma_\varepsilon$ being the standard deviation of the model residuals. We made sure that $0.25 < P_{Gfir} < 0.75$ to comply with the definition of mixture that we use in this study. Another random number was drawn and added to the model prediction until this condition was met. $G_{spruce}$ was then obtained by substracting $G_{fir}$ to $G_t$.

@@

We assigned species quadratic diameter ($Dg_{sp}$) in different ways depending on the stand composition. In the case of pure stands, we directly used the total quadratic diameter ($Dg_t$) calculated from LIDAR data. We developed a three-step procedure for mixed stands:

@@

  where $Dg_i$ and $Dg_j$ are the quadratic diameters of species $i$ and $j$; $\alpha$ and $\beta_{1-X}$, parameters to estmiate; and $\varepsilon$, the model residuals. Here, we used $Dg_i$ and $Dg_j$ obtained from "true mixtures", i.e. PROTEST plots where the two mixed species represented more than 75\% of the total basal area, and this, before the grouping of species. We applied the same variable selection procedure as the one we applied to the site index model (see the three final models in SI).

  \item We then calculated $r_{Dg}$, the $Dg_i / Dg_j$ ratios for all mixed stand over the study area by adding to the models predictions a random number drawn from the normal distribution $\mathcal{N} (0, \sigma_\varepsilon)$, with $\sigma_\varepsilon$ being the standard deviation of the models residuals. We made sure that $r_{Dg}$ falled in the range of the $Dg_i / Dg_j$ ratio values directly measured in the PROTEST "true mixtures" to avoid producing stands with unbalanced diameters for both species. Another random number was drawn and added to the models predictions until this condition was met.

@@

\noindent The three starting equations are as follows

@@

\noindent where $r_{Dg}$ is calculated by adding to the models predictions (described at eqn \ref{DgModel}) a random number (see the \textit{Species quadratic diameter} section).

>>>>

        \item Finally, we removed (one by one) the variables whose effect became non-significant following the addition of the quadratic effects starting with the least significant ones untill all variables were significant (see the four final species-specific models in SI).

@@

    \item First we classified the PROTEST plots into 7 compositions (corresponding to the compositions that will be simulated): 4 pure compositions (beech, oak, fir, spruce; when these species represented more than 75\% of the plots total basal area) and 3 mixed compositions (beech-fir, beech-spruce, fir-spruce; when these species were the 2 most abundant on the plots and represented (together) more than 75\% of the plots total basal area). However, because other species than our 4 target species were present on the study area (ref composition / species abundance?), we previously grouped some species together as follows:

@@

    \item Finally, to assign a composition to a forest plot located in a specific TFV type, we randomly selected a composition from the list of compositions associated to this TFV type while complying with the composition type allready assigned to the plot (i.e. deciduous, coniferous or deciduous-coniferous mixture). Thus plots classified as deciduous could be assigned 2 compositions: beech or oak; plots classified as coniferous could be assigned 3 compositions: fir, spruce or fir-spruce mixture; and plots classified as deciduous-coniferous mixture could be assigned 2 compositions: beech-fir or beech-spruce.

@@

\noindent We assigned species basal area values ($G_{sp}$) to each forest plot using the stand total basal area ($G_t$) and the proportion of deciduous basal area ($P_{Gd}$) calculated from LIDAR data. $G_{sp}$ could directly be derived from these measures for pure stands and deciduous-coniferous mixtures (i.e. beech-fir and beech-spruce stands). We developed a two-step procedure to assign $G_{sp}$ to conifer mixtures (i.e. fir-spruce mixtures):

@@

  \noindent where $\alpha$ and $\beta_{1-X}$ are parameters to estmiate and $\varepsilon$, the model residuals. We applied the same variable selection procedure as the one we applied to the site index model (see final model in SI). Here, we used $G_{fir}$ and $G_{spruce}$ obtained from "true fir-spruce mixtures" and after having assigned the basal area of non-target species to the target species (see the \textit{composition initialisation} section). "True mixtures" were PROTEST plots where the two mixed species represented more than 75\% of the total basal area before the grouping of species.

  \item We then calculated $P_{Gfir}$, the proportion of $G_{fir}$ for all conifer mixtures over the study area by adding to the model predictions a random number drawn from the normal distribution $\mathcal{N} (0, \sigma_\varepsilon)$, with $\sigma_\varepsilon$ being the standard deviation of the model residuals. We made sure that $0.25 < P_{Gfir} < 0.75$ to comply with the definition of mixture that we use in this study. Another random number was drawn and added to the model prediction until this condition was met. $G_{fir}$ and $G_{spruce}$ could then be calculated from $P_{Gfir}$ and $G_t$.

@@

We assigned species quadratic diameter ($Dg_{sp}$) to each forest plot in different ways depending on the stand composition. In the case of pure stands, we directly used the total quadratic diameter ($Dg_t$) calculated from LIDAR data. We developed a three-step procedure for mixed stands:

@@

  where $Dg_i$ and $Dg_j$ are the quadratic diameters of species $i$ and $j$; $\alpha$ and $\beta_{1-X}$, parameters to estmiate; and $\varepsilon$, the model residuals. Here, we used $Dg_i$ and $Dg_j$ obtained from "true mixtures", i.e. PROTEST plots where the two mixed species represented more than 75\% of the total basal area, and this, before the grouping of species. We applied the same variable selection procedure as the one we applied to the site index model (see the three mixture-specific final models in SI).

  \item We then calculated $r_{Dg}$, the $Dg_i / Dg_j$ ratios for all mixed stand over the study area by adding to the models predictions a random number drawn from the normal distribution $\mathcal{N} (0, \sigma_\varepsilon)$, with $\sigma_\varepsilon$ being the standard deviation of the models residuals. We made sure that $r_{Dg}$ falled in the range of the $Dg_i / Dg_j$ ratio values directly measured in the PROTEST "true mixtures" to avoid producing stands with excessively unbalanced diameters for both species. Another random number was drawn and added to the models predictions until this condition was met.

@@

\noindent The three starting equations are as follows:

@@

\noindent where $r_{Dg}$ is calculated by adding to the models predictions (models described at eqn \ref{DgModel}) a random number drawn from the normal distribution $\mathcal{N} (0, \sigma_\varepsilon)$, with $\sigma_\varepsilon$ being the standard deviation of the models residuals (see the \textit{Species quadratic diameter} section).
